---
title: "Shiny project for Motor Trend Car Road Tests"
author: "Aijun Zhang"
date: "2023-06-01"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

- Problem: Exploring the relationship between variables in the mtcars data set.

  Please see the variables: <br>
  mpg	  Miles/(US) gallon &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;|  cyl  Number of cylinders <br>
  disp	Displacement (cu.in.) &nbsp;&nbsp;|  hp  	Gross horsepower <br>
  drat	Rear axle ratio &nbsp;&nbsp;&nbsp;&nbsp;|  wt	  Weight (1000 lbs) <br>
  qsec	1/4 mile time &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;|  carb	Number of carburetors <br>
  vs	  Engine (0 = V-shaped, 1 = straight) <br>
  am	  Transmission (0 = automatic, 1 = manual) <br>
  gear	Number of forward gears
  
- Solution: Interactive scatter plot using Shiny .
- Benefits: Easy data visualization and analysis.

## How It Works

- Select the variable for the X-axis.
- Adjust the range of the X-axis using the slider.
- The scatter plot updates automatically.
- Dots are color-coded based on "am" values (<span style="color: red;">red</span> dots are automatic; <span style="color: blue;">blue</span> manual).

## Demo of the Shiny website
```{r, echo=FALSE}
knitr::include_app("https://aijun.shinyapps.io/Project001/")
```

## Conclusion

- Interactive exploration of the mtcars dataset.
- Easy visualization and analysis of variable relationships.
- Try it out and gain insights from the URL below

https://aijun.shinyapps.io/Project001/

Thanks!
